Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2014-10-29 Papers/InProgress/LogicAndReligionCongress/Abstract.tex
Add formalizations of Hajek's three emendations

\section{Hájek's Second Emendation \AOEHH} \label{apx:Hajek2}

\section{Hájek's Third Emendation \AOEHHH} \label{apx:Hajek3}

>>>>

% \begin{figure}[t]
% \noindent \framebox[\columnwidth][r]{
% \begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are necessarily implied by a positive property: 
  $$\hol{G_H(x) \equiv \forall \varphi [\nec \varphi(x) \biimp \exq \psi[P(\psi) \wedge \nec \allq x [\psi(x)  \imp \varphi(x))]]}$$ 
\item[A3']  The property of being God-like is positive: 
  $$\hol{P(G_H)}$$
\item[A4]  Positive properties are necessarily positive: 
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$ 
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$ 
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences: 
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[A5'] Necessary existence is a positive property: $$\hol{P(\NE_A)}$$

\item[L3] 
  \begin{itemize}
  \item[(1)] The negation of a positive property is not positive:
$$\hol{\allq \varphi[P(\varphi) \imp \neg P(\neg \varphi)] }$$
  \item[(2)] Positive properties are possibly exemplified:
$$\hol{\allq \varphi[P(\varphi) \imp \pos \exq x \varphi(x)] }$$
  \item[(3)] If a god-like being exists, then necessarily a god-like being exists:
$$\hol{\allq x[G_H(x) \imp \nec G_H(x)))] }$$  
  \item[(4)] All positive properties are necessarily implied by the property of being god-like:
$$\hol{\allq \varphi[P(\varphi) \imp \nec \allq x[G_H(x) \imp \varphi(x)]] }$$
  \end{itemize}
\item[L4]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G_H(x) \imp \ess{G_H}{x}]}$$

\item[T3'] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_H(x)}$$
% 
\end{itemize}
% \end{minipage}
% } \vskip-.5em
% \caption{Anderson's Emendation \cite{ToDo:Anderson}.\label{fig:anderson}} 
% \end{figure}

\section{Hájek's Second Emendation \AOEHH} \label{apx:Hajek2}
% \begin{figure}[t]
% \noindent \framebox[\columnwidth][r]{
% \begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[A:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive: 
  $$\hol{G_A(x) \equiv \forall \varphi [P(\varphi) \biimp \nec \varphi(x)]}$$ 
\item[H:A3]  The property of being God-like and existing actually is positive: 
  $$\hol{P(G_A \wedge E)}$$
\item[T3'] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_A(x)}$$
% 
\end{itemize}
% \end{minipage}
% } \vskip-.5em
% \caption{Anderson's Emendation \cite{ToDo:Anderson}.\label{fig:anderson}} 
% \end{figure}

\section{Hájek's Third Emendation \AOEHHH} \label{apx:Hajek3}
% \begin{figure}[t]
% \noindent \framebox[\columnwidth][r]{
% \begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are necessarily implied by a positive property: 
  $$\hol{G_H(x) \equiv \forall \varphi [\nec \varphi(x) \biimp \exq \psi[P(\psi) \wedge \nec \allq x [\psi(x)  \imp \varphi(x))]]}$$ 
\item[D4]  A property is positive\textsuperscript{\#} iff it is necessarily implied by a positive property: 
  $$\hol{P^\#(\varphi) \equiv \exq \psi[P(\psi) \wedge \nec \allq x[\psi(x) \imp \varphi(x)]]}$$
\item[A3']  The property of being God-like is positive: 
  $$\hol{P(G_H)}$$
\item[H:A4]  Positive\textsuperscript{\#} properties are necessarily positive\textsuperscript{\#}: 
  $$\hol{\allq \varphi [P^\#(\varphi) \imp \Box \; P^\#(\varphi)]}$$ 
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$ 
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences: 
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[H:A5] Necessary existence is a positive\textsuperscript{\#} property: $$\hol{P^\#(\NE_A)}$$ 
% 
\end{itemize}
% \end{minipage}
% } \vskip-.5em
% \caption{Anderson's Emendation \cite{ToDo:Anderson}.\label{fig:anderson}} 
% \end{figure}
